---
title: "Mapping Human Genes to Mice Genes"
author: "Jonathan Zhang"
date: "6/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(xlsx)
```

## The Task
* Find the mouse homolog to each human ligand and receptor
* Export the homologs in the form of an edgelist, with the mouse ligand on one column with the human ligand to the right
  + Adjacent to the 2 ligand columns will be 2 receptor columns
  + Multiple matches for mouse genes will result in concatenated genes separated by a space
  + If no match is found, NA will be the value
  + Ligands and receptors correspond in a row
  + Final product is an xlsx
  
### Initial Resources
* A list Z of 2557 obs. with 4 variables (Ligand.ApprovedSymbol, Ligand.Name Receptor.ApprovedSymbol, Receptor.Name) showing human ligands and their corresponding receptors
* A xlsx file which has 20947 rows with 4 columns (geneSymbol.mm, geneSymbol.hg, entrezId.mm, entrezId.hg) showing the gene homologs between mice and humans

```{r, eval = FALSE}
ligandgene.hg = Z$Ligand.ApprovedSymbol
receptorgene.hg = Z$Receptor.ApprovedSymbol
homologs = read.xlsx(file = "homolog.xlsx", sheet = 1, sheetName = "mouse_human")
humanmap = ctrlf$geneSymbol.hg
humanmap = as.character(humanmap)
mousemap = ctrlf$geneSymbol.mm
mousemap = as.character(mousemap)
```

```{r, eval = FALSE}
ligandgene.mm = list()
for (i in 1:length(ligandgene.hg)) {
    temp = which(humanmap == ligandgene.hg[i])
    whichtemp = character(0)
    for (k in 1:length(temp)) {
        whichtemp = paste(whichtemp, mousemap[temp[k]], collapse = " ")
    }
    ligandgene.mm[[i]] = whichtemp
    rm(temp)
    rm(whichtemp)
}
ligandgene.mm = as.character(ligandgene.mm)
ligandgene.mm[ligandgene.mm == " NA "] = NA_character_
ligandgene.mm = trimws(ligandgene.mm)
ligandmap = data.frame(ligandgene.hg,ligandgene.mm)

receptorgene.mm = list()
for (i in 1:length(receptors)) {
    temp = which(humanmap == receptors[i])
    whichtemp = character(0)
    for (k in 1:length(temp)) {
        whichtemp = paste(whichtemp, mousemap[temp[k]], collapse = " ")
    }
    receptorgene.mm[[i]] = whichtemp
    rm(temp)
    rm(whichtemp)
}
receptorgene.mm = as.character(receptorgene.mm)
receptorgene.mm[receptorgene.mm == " NA "] = NA_character_
receptorgene.mm = trimws(receptorgene.mm)
receptormap = data.frame(receptors,receptorgene.mm)


write.xlsx(data.frame(ligandgene.hg, ligandgene.mm, receptorgene.hg, receptorgene.mm),"hg-mm-ligandreceptor-homologs.xlsx", row.names= FALSE)
```

## Result
The task was accomplished. The variables ligandmap and receptormap (length 2557), can be used for further manipulation.