---
title: "Seurat Functions"
author: "Jonathan Zhang"
date: "7/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Seurat)
library(gplots)
library(ggcorrplot)
```

<<<<<<< HEAD
Note: My Seurat object is stored in d, and d_mica is a branched form of d, while d is kept as a reference just in case. 
d_aux is created in corr() as another branch.
Seurat Version: 2.3.4
=======
Note: My Seurat object is stored in d, and d_mica is a branched form of d, while d is kept as a reference just in case. d_aux is created in corr() as another branch.
>>>>>>> 7f83c5949c082c6a8b4122d4c40158cbf853e34f

## Visualization Functions
These simple functions made it easier to pull up vln plots and tSNE graphs instead of having to repaste longer function calls.

```{r}
vln = function(...) {
    genes = list(...)
    VlnPlot(d,features.plot=unlist(genes))
}
tsne = function(...) {
    genes = list(...)
    FeaturePlot(object = d, features.plot = unlist(genes), cols.use = c("grey", "blue"), reduction.use = "tsne")
}
corr = function(...) {
    pick_genes <<- unlist(list(...))
    d_aux = d_mica
    d_aux@ident = factor(as.character(d_mica@ident))
    
    Z = as.matrix(d_aux@data[pick_genes,])
    
    avg_markers_expr <<- matrix(NA, length(table(d_aux@ident)), length(pick_genes))
    rownames(avg_markers_expr) <<- names(table(d_aux@ident))
    colnames(avg_markers_expr) <<- pick_genes
    
    for (clust in names(table(d_aux@ident))){
        iclust = which(d_aux@ident == clust)
        for (g in pick_genes){
            avg_markers_expr[as.character(clust),g] <<- mean(Z[g,iclust])
        }
    }
    
    corr1 <<- cor(t(avg_markers_expr))
    corr2 <<- cor(avg_markers_expr)
}
plotcorr = function (correlation) { # meant to be used after corr() with corr1 and corr2 as parameters
    ggcorrplot(correlation, hc.order = TRUE, outline.col = "white")
} 
heat = function () { # meant to be used after corr() with no parameter since avg_markers_expr is already set
	heatmap.2(avg_markers_expr)
}
heatc = function (custom_heat) { # custom heatmap parameter
	heatmap.2(custom_heat)
}
```

## Downsampling for DE (Differentially Expressed) Genes
https://github.com/satijalab/seurat/issues/1794

Seurat has functions FindMarkers() and FindAllMarkers() functions help find differentially expressed genes by comparing 
clusters or groups of clusters. However, some differentially expressed genes are ubiquitous but still detected as DE genes 
due to maybe a higher expression in one cluster than the other (obviously, ubiquitous genes will not help classify clusters). 
Also, other genes are simply unhelpful for cluster differentiation. 

By curating a gene database with relevant genes, we can cross reference the DE genes with our database and filter the list 
of DE genes to only those that are included in the database. In the case of immunophenotyping, the database would include 
all clusters of differentiation (CD/Cd markers) and key transcription factors in immune cells.

This way, I can concentrate on DE genes that will actually help me identify the phenotype of a cluster.

To begin downsampling, simply create a character vector with the curated gene names.

```{r, eval = FALSE}
curated = c() # add genes here or extract from other source
de_genes = FindMarkers(d, ident.1 = 1, ident.2 = c(3:5)) # replace with your own idents and parameters
# https://satijalab.org/seurat/v3.0/pbmc3k_tutorial.html shows you how to use FindMarkers
de_genes$rows = rownames(de_genes)
de_genes = de_genes[de_genes$rows %in% curated]
```

## Handy Functions
https://github.com/satijalab/seurat/issues/771 

```{r, eval = FALSE}
# Solution to GitHub issue
for (i in 1:30) {
	d = RenameIdent(d, old.ident.name = old[i], new.ident.name = new[i])
}
```