---
title: "Sorting Gene Database"
author: "Jonathan Zhang"
date: "6/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R.matlab)
library(dplyr)
# library(xlsx) -need to download java and set JAVA_HOME variable
```

``` {r, eval = FALSE}
# Some Notes:
  # fix rmarkdown runtime issue with the plots
  # some combinations of protein A, protein B, and mode were the same but there were multiple scores (basically same pairing but different scores), so the highest one was taken.
```

## Task
* Extract all pairings involving a mouse ligand and receptor
* Save the data for public use

## Variable Definitions
1. **ligands.mm** : vector containing gene names of mouse ligands [412 elements]
2. **receptors.mm** : vector containing gene names of mouse receptors [2,332 elements]
3. **dict** : data frame with general gene / protein data for the database [270412 elements]
  + _GeneID_ : vector of genes by their ID [67,603 elements]
  + _GeneName_ : vector of genes by their name [67,603 elements]
  + _ProteinID_ : vector of respective proteins expressed by genes [67,603 elements]
  + _MGI.sym_ : vector of genes by their MGI Accession ID
4. **pairID** : data frame with gene pairings as edgelist of their IDs along with the mode of interaction and score [3,041,178 elements]
  + _pA_ : vector of first genes' IDs [1,013,726 elements]
  + _pB_ : vector of second genes' IDs [1,013,726 elements]
  + _mode_ : vector of type of interaction [1,013,726 elements]
  + _score_ : vector of score which indicates reliability [1,013,726 elements]
5. **pairGene** : data frame with gene pairings as edgelist of their gene names along with the mode of interaction [3,041,178 elements]
  + _pA_Gene_ : vector of first genes' names [1,013,726 elements]
  + _pB_Gene_ : vector of second genes' names [1,013,726 elements]
  + _mode_ : vector of type of interaction [1,013,726 elements]
  + _score_ : vector of score which indicates reliability [1,013,726 elements]
6. **Z** : list of all of the data from the `.mat` file detailing the gene interactions (converted with `readmat()`)

### Visualizing the Database

```{r modes, eval = FALSE}
modev = as.factor(as.vector(unlist(Z$mode))) 
modeplot = summary(modev)
modeplot = modeplot[order(modeplot)]
barplot(modeplot, las = 2)
print(modeplot)
```

```{r scores, eval = FALSE}
hist(Z$score)
summary(Z$score)
```

### Manipulating the Dataframe

```{r, eval = FALSE}
names = vector(mode="character")
master = data.frame(pairGene$pA_Gene,pairGene$pB_Gene,pairGene$mode, pairGene$score, pairID$pA, pairID$pB)
names(master) = c("pA_Gene","pB_Gene","mode","score","pA_ID","pB_ID")
x = unique(master)
x = x[order(x$score, decreasing = TRUE),]
x = distinct(x, pA_Gene, pB_Gene,mode, .keep_all = TRUE) # eliminates duplicates without considering score [603061 elements]
for (i in 1:length(x$score)) { # stores unique row names made of gene names and mode
    names[i] = paste(x$pA_Gene[i], x$pB_Gene[i], x$mode[i], x$score[i], collapse = " ")
}
rownames(x) = names # assigns the row names
```

Now we arrive at a dataframe with no duplicate combinations of protein A, protein B, and mode. 

### Searching the List

```{r, eval = FALSE}
p1 = x$pA_Gene 
temp = p1 %in% ligands.mm 
xligandsA = x[which(temp==TRUE),] # extracts all pairs where pA = ligand
p1B = xligandsA$pB_Gene # vector of pB where corresponding pA = ligand
temp = p1B %in% receptors.mm 
ligands_A = xligandsA[which(temp == TRUE),] # data frame where pA = ligand and pB = receptor

p2 = x$pB_Gene 
temp = p2 %in% ligands.mm 
xligandsB = x[which(temp==TRUE),] # extracts all pairs where pB = ligand
p2A = xligandsB$pA_Gene # vector of pA where corresponding pB = ligand
temp = p2A %in% receptors.mm 
ligands_B = xligandsB[which(temp == TRUE),] # data frame where pA = receptor and pB = ligand

rm(temp, i)

ligands_B = ligands_B[c(2,1,3,4,5,6)]
names(ligands_B) = c("pA_Gene","pB_Gene","mode","score","pA_ID","pB_ID")
ligands_A$rows = rownames(ligands_A)
ligands_B$rows = rownames(ligands_B)
pairs = union(ligands_A,ligands_B)
pairs = distinct(pairs, pA_Gene, pB_Gene, mode, .keep_all = TRUE)
rownames(pairs) = pairs$rows
pairs = subset(pairs,select = -c(rows))
```

# Visualizing the Final Data

```{r, eval = FALSE}
modef = as.factor(pairs$mode) 
modepairs = summary(modef)
modepairs = modepairs[order(modepairs)]
barplot(modepairs, las = 2)
print(modepairs)
```

```{r, eval = FALSE}
hist(pairs$score)
summary(pairs$score)
```
