---
title: "Nodes and Connections"
author: "Jonathan Zhang"
date: "6/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(spatstat)
```

## Task 1
* Initialize 1000 nodes in a data structure
* Using a binary system, make connections between nodes with a success rate of 5%
  + 1 means that a connection is present between two nodes
  + 0 means that there is no connection
* Plot a histogram of each node's number of connections
  + Make observations about the distribution
  
The following plot is meant to visualize the 1000 nodes (not representative of real values).

```{r, echo=FALSE}
plot(runifpoint(1000, win=owin(c(0,1),c(0,1)), giveup=1000), main = '1000 Node Visualization (1x1)')
```

### Generating the Matrix

```{r}
mat = matrix(runif(1000000),1000)
for(row in 1:nrow(mat)) {
  for(col in row:ncol(mat)) {
      if (mat[row,col] < 0.05 && row != col){
        mat[row,col] = 1
        mat[col,row] = 1
      } else {
        mat[row,col] = 0
        mat[col,row] = 0
      }
  }
}
```

### Generating the Histogram of Connections

```{r}
data1 = rowSums(mat)
hist(data1)
summary(data1)
```

### Some Stats

```{r, eval = FALSE}
qqnorm(data1)
qqline(data1)
```

## Task 2
* Randomly pick a node and record the number of connections
* Reiterate 1000 times and plot a histogram
  + Make observations about the distribution

### Generating the Histogram of Connections

```{r}
data2 = vector(mode = "numeric", length = 1000)
for (i in 1:1000) {
  x = trunc(runif(1,0,1000) + 1)
  y = sum(mat[x,])
  data2[i] = y
}
hist(data2)
summary(data2)
```

### Some Stats

```{r, eval = FALSE}
qqnorm(data1)
qqline(data1)
```

## Task 3
* Generate a path starting with a random node, only moving along connections (but not backwards)
  + Move along 1000 times, but end when a node has no further connections besides the one previously traversed (highly unlikely)
* Along each node on the path, record the number of connections
* Plot a histogram
  + Make observations about the distribution

```{r}
data3 = vector(mode = "numeric")
start = trunc(runif(1,0,1000) + 1)
list = which(mat[start,] == 1)
back = sample(list, 1)
for (k in 1:1000) {
  node = back
  list = which(mat[node,] == 1)
  tempback = back
  while (tempback == back) {
    back = sample(list, 1)
  }
  data3 = c(data3, sum(mat[node,]))
}
hist(data3)
summary(data3)
```

## Task 4
* Count the number of potential triangles in the graph

A triangle needs 3 distinct nodes, and the 3 nodes cannot be collinear (which is negligible due to dimensionality). Therefore, the number of 3 node combinations can be calculated as long as there are connections between the 3.

### Answer 

```{r}
ans = 0
for (p in 1:1000) {
  list = which(mat[p,] == 1)
  ans = ans + (sum(mat[list,list]) / 2)
}
print(ans / 3)
```
